Survival Compass

### 2024-04-20 paper/paper.qmd
playing around with some new figures for results section

  ggplot(tumor_size_counts, aes(x = tumor_size, y = percentage)) +
    geom_bar(stat = "identity", fill = "purple") +
    labs(title = "Graph 4: Tumor Size",
         x = "",
         y = "") +  # Remove y-axis label 
    theme_minimal() +
    theme(
      text = element_text(family = "patrick"), # Set font to Patrick Hand
      axis.title.y = element_blank() # Remove y-axis title
    )
)

@@

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

>>>>

  ggplot(tumor_size_counts, aes(x = tumor_size, y = percentage)) +
    geom_bar(stat = "identity", fill = "purple") +
    labs(title = "Graph 4: Tumor Size",
         x = "",
         y = "") +  # Remove y-axis label 
    theme_minimal() +
    theme(
      text = element_text(family = "patrick"), # Set font to Patrick Hand
      axis.title.y = element_blank() # Remove y-axis title
    ) + guides(color = guide_legend(title.position = "top", title.vjust = 0.5))  
    # Adjust legend title position

)

@@

```{r}
##| echo: false
#| eval: true
#| warning: false
#| message: false

# install.packages
# install.packages("reshape2")
# install.packages("vcd")

# Load required libraries
library(ggplot2)
library(arrow)
library(dplyr)
library(showtext)
library(reshape2)
library(vcd)
library(patchwork)

# Create a scatter plot with trend lines - pathologic stage vs. time vs. treatment type
ggplot(data = analysis_data, aes(x = days_to_death, y = pathologic_stage, color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  # Adjusted point size and transparency
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type), alpha = 0.3) +  
  # Adjust trend line transparency
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue", "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Pathologic Stage", color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500))+  # Set breaks on x-axis
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), 
        # Set font to Patrick Hand and increase the size
      legend.position = "bottom", legend.text = element_text(size = 12)) +  
  # Adjust legend position and text size
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5))  
  # Adjust legend title position

# Create a scatter plot with trend lines - presence of distant metastasis vs. time vs. treatment type
ggplot(data = analysis_data, aes(x = days_to_death, y = presence_of_distant_metastasis, color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  # Adjusted point size and transparency
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type), alpha = 0.3) +  
  # Adjust trend line transparency
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue", "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Presence of Distant Metastasis", color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) +  # Set breaks on x-axis
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), 
        # Set font to Patrick Hand
      legend.position = "bottom", legend.text = element_text(size = 12)) +  
  # Adjust legend position and text size
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5))  
  # Adjust legend title position

# Create a scatter plot with trend lines - lymph node involvement vs. time vs. treatment type
ggplot(data = analysis_data, aes(x = days_to_death, y = lymph_node_involvement, color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  # Adjusted point size and transparency
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type), alpha = 0.3) +  
  # Adjust trend line transparency
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue", "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Lymph Node Involvement", color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) +  # Set breaks on x-axis
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), # Set font to Patrick Hand
      legend.position = "bottom", legend.text = element_text(size = 12)) +  
  # Adjust legend position and text size
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5))  
  # Adjust legend title position

# Create a scatter plot with trend lines - tumor size vs. time vs. treatment type
ggplot(data = analysis_data, aes(x = days_to_death, y = tumor_size, color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  # Adjusted point size and transparency
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type), alpha = 0.3) +  
  # Adjust trend line transparency
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue", "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Tumor Size", color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) +  # Set breaks on x-axis
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), # Set font to Patrick Hand
      legend.position = "bottom", legend.text = element_text(size = 12)) +  
  # Adjust legend position and text size
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5))  
  # Adjust legend title position

# install.packages
# install.packages("reshape2")
# install.packages("vcd")

# Load required libraries
library(ggplot2)
library(arrow)
library(dplyr)
library(reshape2)
library(vcd)

# Create a ggplot2 plot for pathologic_stage and treatment_type with adjusted margins, legend, and horizontal y-axis labels
ggplot(analysis_data, aes(x = pathologic_stage, fill = treatment_type)) +
  geom_bar(position = "fill") +
  theme(axis.text.x = element_blank(), axis.text.y = element_text(angle = 0, hjust = 1)) +
  scale_fill_manual(name = "Treatment Type", values = c("Pharmaceutical Therapy, NOS" = "blue", "Radiation Therapy, NOS" = "red"))

@@
